Tracing the Meta-Level: PyPy's Tracing JIT Compiler

### 2009-06-09 talk/icooolps2009/paper.tex
add acknowledgements
change the acks slightly
Simplify hints a bit, and add a footnote that it is different in reality. They confused reviewers quite a bit.

In addition to the classification of the variables, there are two methods of
\texttt{JitDriver} that need to be called. Both of them receive as arguments the
current values of the variables listed in the definition of the driver. The
first one is \texttt{jit\_merge\_point} which needs to be put at the beginning
of the body of the bytecode dispatch loop. The other, more interesting one, is
\texttt{can\_enter\_jit}. This method needs to be called at the end of any
instruction that can set the program counter of the language interpreter to an
earlier value. For the example this is only the \texttt{JUMP\_IF\_A}
instruction, and only if it is actually a backward jump. Here is
where the language interpreter performs profiling to decide
when to start tracing. It is also the place where the tracing JIT checks
whether a loop is closed. This is considered to be the case when the values of
the ``green'' variables are the same as at an earlier call to the
\texttt{can\_enter\_jit} method.

@@

>>>>

In addition to the classification of the variables, there are two methods of
\texttt{JitDriver} that need to be called. The
first one is \texttt{jit\_merge\_point} which needs to be put at the beginning
of the body of the bytecode dispatch loop. The other, more interesting one, is
\texttt{can\_enter\_jit}. This method needs to be called at the end of any
instruction that can set the program counter of the language interpreter to an
earlier value.\footnote{The hints need to be written a bit differently in the
actual implementation for purely technical reasons.} For the example this is
only the \texttt{JUMP\_IF\_A}
instruction, and only if it is actually a backward jump. Here is
where the language interpreter performs profiling to decide
when to start tracing. It is also the place where the tracing JIT checks
whether a loop is closed. This is considered to be the case when the values of
the ``green'' variables are the same as at an earlier call to the
\texttt{can\_enter\_jit} method.

@@

\section*{Acknowledgements}
The authors would like to thank Michael Leuschel, Toon Verwaest and the
referees of ICOOOLPS'09 for helpful comments on earlier versions of this paper.
